SU($n$) spin model dynamics

### 2020-10-20 sun_phases/sun_dynamics_notes.tex
changed some conventions, and re-ordered table listing possible drive hamiltonians

Perhaps more interestingly, we can in principle prepare inhomogeneous product states in which the state of each spin is correlated with its corresponding single-body term of the spin Hamiltonian in \eqref{eq:spin_pair}.
We are currently working on characterizing the sort of inhomogeneous states that we can prepare.

@@

% Motivations / background:
% https://arxiv.org/pdf/1901.06282.pdf
% https://arxiv.org/abs/1911.00099
% https://arxiv.org/abs/2005.10910
% https://journals.aps.org/pra/abstract/10.1103/PhysRevA.86.012118
% https://journals.aps.org/pra/abstract/10.1103/PhysRevA.94.010301
% https://arxiv.org/pdf/2003.08668.pdf
% https://www.osapublishing.org/ol/abstract.cfm?uri=ol-44-10-2558

@@

Denoting the polar and azimuthal angles of $\v v$ respectively by $\alpha_{\v v}$ and $\beta_{\v v}$, we can use the fact that $s_\x,s_\y,s_\z$ form an $\su(2)$ algebra to expand

@@

  &= e^{-\i\beta_{\v v}s_\z} e^{-\i\alpha_{\v v}s_\y}
  s_\pm e^{\i\alpha_{\v v}s_\y} e^{\i\beta_{\v v}s_\z} \\
  &= -\sin\alpha_{\v v}\, s_\z
  + \f12 \p{\cos\alpha_{\v v}+1} e^{\mp\i\beta_{\v v}} s_\pm
  + \f12 \p{\cos\alpha_{\v v}-1} e^{\pm\i\beta_{\v v}} s_\mp.

@@

  - \p{\Omega_+ - \Omega_-}^2 s_{\tilde\eta_0,\y}^2
  ,

@@

\begin{table}
  \centering
  \caption{Drive Hamiltonians that can be implemented with various amplitude-matching conditions when all $\eta_m=0$.
    Here $\v s_{\t{3D}}^2=s_\x^2+s_\y^2+s_\z^2=I\p{I+1}$ is a constant.}
  \begin{tabular}{c|c}
    $(\tilde\Omega_0,\tilde\Omega_+,\tilde\Omega_-)/\sqrt{\Delta}$
    & $H_{\t{drive}}^{\t{single}}$
    \\ \hline\hline
    $\p{1,0,0}$ & $-s_\z^2$
    \\ \hline
    $\p{0,1,0}$ & $-s_\x^2$
    \\ \hline
    $\p{0,0,1}$ & $-s_\y^2$
    \\ \hline
    $\p{0,1,\pm1}$ & $\pm s_\z + s_\z^2 - \v s_{\t{3D}}^2$
    \\ \hline
    $\p{1,0,\pm1}$ & $\pm s_\x + s_\x^2 - \v s_{\t{3D}}^2$
    \\ \hline
    $\p{1,\pm1,0}$
    & $\pm\p{s_\z s_\x+s_\x s_\z} + s_\y^2 - \v s_{\t{3D}}^2$
  \end{tabular}
  \label{tab:drives}
\end{table}

@@

>>>>

Perhaps more interestingly, we can in principle prepare inhomogeneous product states in which the state of each spin is correlated with its corresponding single-body term of the spin Hamiltonian in \eqref{eq:spin_pair}.
We are currently working on characterizing the sort of inhomogeneous states that we can prepare (see Appendix \ref{sec:init_states}).

@@

@@

Denoting the azimuthal and polar angles of $\v v$ respectively by $\alpha_{\v v}$ and $\beta_{\v v}$, we can use the fact that $s_\x,s_\y,s_\z$ form an $\su(2)$ algebra to expand

@@

  &= e^{-\i\alpha_{\v v}s_\z} e^{-\i\beta_{\v v}s_\y}
  s_\pm e^{\i\beta_{\v v}s_\y} e^{\i\alpha_{\v v}s_\z} \\
  &= -\sin\beta_{\v v}\, s_\z
  + \f12 \p{\cos\beta_{\v v}+1} e^{\mp\i\alpha_{\v v}} s_\pm
  + \f12 \p{\cos\beta_{\v v}-1} e^{\pm\i\alpha_{\v v}} s_\mp.

@@

  - \p{\Omega_+ - \Omega_-}^2 s_{\tilde\eta_0,\y}^2,

@@

\begin{table}
  \centering
  \caption{Drive Hamiltonians that can be implemented with various amplitude-matching conditions when all $\eta_m=0$.
    Here $\v s_{\t{3D}}^2=s_\x^2+s_\y^2+s_\z^2=I\p{I+1}$ is a constant and $\sigma\in\set{+1,-1}$.  For each $m\in\set{0,+1,-1}$, a drive with $\abs*{\tilde\Omega_m}=1$ and $\tilde\Omega_n=0$ for $n\ne m$ commutes with drives in which $\tilde\Omega_m=0$ and $\abs*{\tilde\Omega_n}=1$ for $n\ne m$.}
  \begin{tabular}{c|c}
    $(\tilde\Omega_0,\tilde\Omega_+,\tilde\Omega_-)/\sqrt{\Delta}$
    & $H_{\t{drive}}^{\t{single}}$
    \\ \hline\hline
    $\p{1,0,0}$ & $-s_\z^2$
    \\ \hline
    $\p{0,1,0}$ & $-s_\x^2$
    \\ \hline
    $\p{0,0,1}$ & $-s_\y^2$
    \\ \hline
    $\p{0,1,\sigma}$ & $\sigma s_\z + s_\z^2 - \v s_{\t{3D}}^2$
    \\ \hline
    $\p{1,0,\sigma}$ & $\sigma s_\x + s_\x^2 - \v s_{\t{3D}}^2$
    \\ \hline
    $\p{1,\sigma,0}$
    & $\sigma\p{s_\z s_\x+s_\x s_\z} + s_\y^2 - \v s_{\t{3D}}^2$
    \\ \hline
    $\p{1,\sigma,\pm\sigma}$
    & $\pm s_\z \pm \sigma s_\x
    + \sigma \p{s_\z s_\x + s_\x s_\z} - \v s_{\t{3D}}^2$
  \end{tabular}
  \label{tab:drives}
\end{table}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Initial states}
\label{sec:init_states}

Here we explore the preparation of initial states that are correlated with the single-particle terms of the spin Hamiltonian in Eqs.~\eqref{eq:spin_cos} and \eqref{eq:spin_pair}, namely
\begin{align}
  H_{\t{SOC}} \equiv -2 J \sum_{q,\mu} \cos\p{q+\mu\phi} s_{\mu\mu q}.
\end{align}
